Two Mode Networks and Relational Similarity

### 2024-07-13 main.tex
Updates from Overleaf

\begin{figure}[ht!]
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
     \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/p-reflections-sw.png}
            \caption{Reflective centrality trajectories of persons.}
            \label{fig:p-refs}
    \end{subfigure}
     \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/g-reflections-sw.png}
            \caption{Reflective centrality trajectories of groups.}
            \label{fig:g-refs}
    \end{subfigure}
    \caption{Reflective centralities for persons and groups (even reflections)}
    \label{fig:refs}
\end{figure}

@@

\begin{figure}[ht!]
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
     \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/p-reflections-sw.png}
            \caption{Reflective centrality trajectories of persons.}
            \label{fig:p-refs}
    \end{subfigure}
     \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/g-reflections-sw.png}
            \caption{Reflective centrality trajectories of groups.}
            \label{fig:g-refs}
    \end{subfigure}
    \caption{Reflective centralities for persons and groups (even reflections)}
    \label{fig:refs}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth]{Plots/ca-v-bon-reord.png}
    \caption{Southern Women Affiliation matrix with re-ordered rows and columns: (a) row and columns re-ordered according to the person and group score on the first CA dimension, (b) row and columns re-ordered according to person and group Eigenvector centrality score.}
    \label{fig:ca-v-bon}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth]{Plots/ca-eigvec.png}
    \caption{CA Eigenvector plot for persons (a) and groups (c). The first CA score is on the x-axis, and the rank order of persons and groups is on the y-axis. Insets show the eigenvalue orderings on the x-axis ($k$) for persons (b) and groups (d).}
    \label{fig:ca-eigvec}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=1.0\textwidth]{Plots/ca-sim.png}
    \caption{CA similarity plots for persons (a) and groups (b) on the left and right top panel. The bottom panel (c) shows the correspondence plot for persons and groups with scores corresponding to the first dimension on the horizontal axis and scores corresponding to the second dimension on the vertical axis.}
    \label{fig:ca-sim}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=1.0\textwidth]{Plots/bon-sim.png}
    \caption{Bonacich dual centrality similarity plots for persons (a) and groups (b) on the left and right top panel. The bottom panel (c) shows the Bonacich eigenvector centrality correspondence plot for persons and groups with scores corresponding to the standard Bonacich eigenvector centrality on the horizontal axis and scores corresponding to the second largest eigenvector of the affiliation matrix on the vertical axis.}
    \label{fig:bon-sim}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.8\textwidth]{Plots/sr-plot.png}
    \caption{Simrank versus CA comparison. Panel (a) shows the affiliation matrix re-ordered according to the first eigenvector of the SVD of the SimRank similarity matrix. Panels (b) and (d) show the corresponding eigenvector and eigenvalue---panels (c) and (e)---plots for persons and groups, respectively, of the SimRank similarity matrix. Panel (f) shows the correspondence plot based on the eigenvector decomposition of the SimRank similarity matrix. Panels (g) and (h) show the Pearson correlation between the scores corresponding to the first eigenvector of the SimRank similarity matrix (on the y-axis) and the scores corresponding to the first CA dimension (on the x-axis).}
    \label{fig:simrank}
\end{figure}

>>>>

\begin{figure}[ht!]
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
     \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/p-reflections.png}
            \caption{Reflective centrality trajectories of persons.}
            \label{fig:p-refs}
    \end{subfigure}
     \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/g-reflections.png}
            \caption{Reflective centrality trajectories of groups.}
            \label{fig:g-refs}
    \end{subfigure}
    \caption{Reflective centralities for persons and groups (even reflections)}
    \label{fig:refs}
\end{figure}

@@

\begin{figure}[ht!]
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
     \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/ca-reord.png}
            \caption{Re-ordered Affiliation matrix (CA).}
            \label{fig:ca-reord}
    \end{subfigure}
     \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/bon-reord.png}
            \caption{Re-ordered Affiliation matrix (Bonacich).}
            \label{fig:bon-reord}
    \end{subfigure}
    \caption{Southern Women Affiliation matrix with re-ordered rows and columns: (a) row and columns re-ordered according to the person and group score on the first CA dimension, (b) row and columns re-ordered according to person and group Eigenvector centrality score.}
    \label{fig:ca-v-bon}
\end{figure}

@@

\begin{figure}
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
     \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/p-ca-eigvec.png}
            \caption{Eigenvector plot (Persons).}
            \label{fig:ca-reord}
    \end{subfigure}
     \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/g-ca-eigvec.png}
            \caption{Eigenvector plot (Groups).}
            \label{fig:bon-reord}
    \end{subfigure}
    \caption{CA Eigenvector plot for persons (a) and groups (b). The first CA score is on the x-axis, and the rank order of persons and groups is on the y-axis. Insets show the eigenvalue orderings on the x-axis ($k$) for persons and groups.}
    \label{fig:ca-eigvec}
\end{figure}

@@

\begin{figure}
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
     \begin{subfigure}[b]{0.425\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/p-ca-sim.png}
            \caption{CA Similarity plot (Persons).}
            \label{fig:p-ca-sim}
    \end{subfigure}
     \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/g-ca-sim.png}
            \caption{CA Similarity plot (Groups).}
            \label{fig:g-ca-sim}
    \end{subfigure} \\
     \begin{subfigure}[b]{0.65\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/ca-corr-plot.png}
            \caption{CA correspondence plot.}
            \label{fig:ca-corr}
    \end{subfigure}
    \caption{CA similarity plots for persons (a) and groups (b) on the left and right top panel. The bottom panel (c) shows the correspondence plot for persons and groups with scores corresponding to the first dimension on the horizontal axis and scores corresponding to the second dimension on the vertical axis.}
    \label{fig:ca-sim}
\end{figure}

@@

\begin{figure}
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
     \begin{subfigure}[b]{0.425\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/p-bon-sim.png}
            \caption{Bonacich Similarity plot (Persons).}
            \label{fig:p-bon-sim}
    \end{subfigure}
     \begin{subfigure}[b]{0.4\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/g-bon-sim.png}
            \caption{Bonacich Similarity plot (Groups).}
            \label{fig:g-bon-sim}
    \end{subfigure} \\
     \begin{subfigure}[b]{0.65\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/bon-corr-plot.png}
            \caption{Bonacich correspondence plot.}
            \label{fig:bon-corr}
    \end{subfigure}
    \caption{Bonacich dual centrality similarity plots for persons (a) and groups (b) on the left and right top panel. The bottom panel (c) shows the Bonacich eigenvector centrality correspondence plot for persons and groups with scores corresponding to the standard Bonacich eigenvector centrality on the horizontal axis and scores corresponding to the second largest eigenvector of the affiliation matrix on the vertical axis.}
    \label{fig:bon-sim}
\end{figure}

@@

\begin{figure}
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/sr-plot-reord.png}
            \caption{Bonacich Similarity plot (Persons).}
            \label{fig:p-bon-sim}
    \end{subfigure}
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/p-sr-plot-eigen.png}
            \caption{Bonacich Similarity plot (Groups).}
            \label{fig:g-bon-sim}
    \end{subfigure} 
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/g-sr-plot-eigen.png}
            \caption{Bonacich correspondence plot.}
            \label{fig:bon-corr}
    \end{subfigure} \\
     \begin{subfigure}[b]{0.6\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/sr.png}
            \caption{Bonacich Similarity plot (Groups).}
            \label{fig:g-bon-sim}
    \end{subfigure} 
     \begin{subfigure}[b]{0.2\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/g-sr-plot-eigen.png}
            \caption{SimRank correspondence plot.}
            \label{fig:sr-corr}
    \end{subfigure}
    \caption{Simrank versus CA comparison. Panel (a) shows the affiliation matrix re-ordered according to the first eigenvector of the SVD of the SimRank similarity matrix. Panels (b) and (d) show the corresponding eigenvector and eigenvalue---panels (c) and (e)---plots for persons and groups, respectively, of the SimRank similarity matrix. Panel (f) shows the correspondence plot based on the eigenvector decomposition of the SimRank similarity matrix. Panels (g) and (h) show the Pearson correlation between the scores corresponding to the first eigenvector of the SimRank similarity matrix (on the y-axis) and the scores corresponding to the first CA dimension (on the x-axis).}
    \label{fig:simrank}
\end{figure}
